---
title: "LaVoy's Landing Page"
output: 
    html_document:
        theme: "darkly"
---

```{r setup, echo=FALSE} 
library(leaflet)
```

# {.tabset}

## Socials

[Github](https://github.com/cyberLaVoy)

[Instagram](https://www.instagram.com/cyberlavoy/)

[LinkedIn](https://linkedin.com/in/cyberLaVoy)

[Goodreads](https://goodreads.com/cyberLaVoy)

[Twitter](https://twitter.com/cyberLaVoy)

[YouTube](https://www.youtube.com/@cyberLaVoy)

## About

An introduction of self...

### Freeskate

Inline skating destinations I've explored.

The number of destination markers will grow!

```{r, echo=FALSE}
destinations <- data.frame(lat = c(33.89, 37.09),
                           lng = c(-118.42, -113.56),
                           desc = c("Marvin Braude", "Virgin River"))

m <- leaflet() %>%
    addTiles() %>%
    addMarkers(lng = destinations$lng,
               lat = destinations$lat,
               popup = destinations$desc)

m
```

## Donate

### BTC

bc1qcwranlzqxwjfrvqqn3al8vysn8ld6y37rsrnyd

### ETH

0x95Ecef0D6a3bb426fFc1f77D11868e52a3e9aAB2

### KAS

kaspa:qp62uzqawhzhutvttzxywxm8fftv6590s42mjwmjn49g6z2l2swr2q0jdxj6x

### IOTX

io14rvz6pdqckm58d7zrf3d49pvah0swv7q7z863u

### DOGE

D9AVH7ia3hgYwZxUKFHWeh1hENBvEDj8WS

### LTC

ltc1q7adhexch7p9xna8a2qdsmnlx9t8uft2wztaxrf