---
title: "LaVoy's Landing Page"
output: 
    html_document:
        theme: "darkly"
---

```{r setup, echo=FALSE} 
library(leaflet)
```

# {.tabset}

## Socials

[Github](https://github.com/cyberLaVoy)

[LinkedIn](https://linkedin.com/in/cyberLaVoy)

[Instagram](https://www.instagram.com/cyberlavoy/)

[Twitter](https://twitter.com/cyberLaVoy)

[YouTube](https://www.youtube.com/@cyberLaVoy)

[Goodreads](https://goodreads.com/cyberLaVoy)

[Letterboxd](https://letterboxd.com/cyberlavoy/)

## About

Hi! I'm LaVoy. 

This section is meant to be filled in with an introduction of who I am... eventually. 

### Places

Some places I've been, doing things I love.

I hope to see the number and spread of location markers grow with time.

```{r, echo=FALSE}
freeskate_destinations <- data.frame(lat = c(33.89, 37.09),
                                     lng = c(-118.42, -113.56),
                                     desc = c("Marvin Braude", "Virgin River"))

jiu_jitsu_training_grounds <- data.frame(lat = c(47.67, 37.12),
                                         lng = c(-122.28, -113.53),
                                         desc = c("Mat Chess", "Ace"))
groups <- c("Freeskate Destinations", "Jiu-Jitsu Training Grounds")
m <- leaflet(width = "100%") %>%
    addTiles() %>%
    addCircleMarkers(lng = freeskate_destinations$lng,
               lat = freeskate_destinations$lat,
               popup = freeskate_destinations$desc,
               group = groups[1],
               color = "#00f",
               fillColor = "#00f") %>%
    addCircleMarkers(lng = jiu_jitsu_training_grounds$lng,
               lat = jiu_jitsu_training_grounds$lat,
               popup = jiu_jitsu_training_grounds$desc,
               group = groups[2],
               color = "#f00",
               fillColor = "#f00") %>%
    addLayersControl(overlayGroups = groups,
                     options = layersControlOptions(collapsed = FALSE))

m
```

## Donate

### BTC

bc1qcwranlzqxwjfrvqqn3al8vysn8ld6y37rsrnyd

### ETH

0x95Ecef0D6a3bb426fFc1f77D11868e52a3e9aAB2

### XMR

4ApQ6VFePy3XG8YGayYWSGSdhBwWM3dkhLHFihzVoAi6QcgkkgU9J3QFfueeP4fEE4giAFuRNjdsj7pJmhvRudrXQyVb2Ta

### KAS

kaspa:qp62uzqawhzhutvttzxywxm8fftv6590s42mjwmjn49g6z2l2swr2q0jdxj6x

### IOTX

io14rvz6pdqckm58d7zrf3d49pvah0swv7q7z863u

### DOGE

D9AVH7ia3hgYwZxUKFHWeh1hENBvEDj8WS

### LTC

ltc1q7adhexch7p9xna8a2qdsmnlx9t8uft2wztaxrf
